---
title: "Journal (reproducible report)"
author: "Gökay Apusoglu"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

Last compiled: `r Sys.Date()`

This page includes the solution for the challange.

# Intro to the tidyverse
## Load libraries
Libraries needed for importing and joining data is loaded :
```{r}
library(tidyverse)
library(readxl)
```
## Importing Files
Data is imported from the specified location :

```{r}
bikes_tbl <- read_excel("data/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
bikeshops_tbl <- read_excel("data/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
orderlines_tbl <- read_excel("data/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
```

Imported bikeshops data :

```{r}
glimpse(bikeshops_tbl)
```

Imported orderlines data :
```{r}
glimpse(orderlines_tbl)
```

## Joining Data
Joining both bikeshops and orderlines data to make the analysis easier :
```{r}
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
```

## Wrangling Data
States and cities are seperated from 'location' column :
```{r}
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # Separation of location column to city and state columns 
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  
  # Calculate total price (price * quantity) and add a total.price column 
  mutate(total.price = price * quantity) %>%
  
  # Columns of interests are selected, reorgonized 
  select(total.price,city,state,order.date)
```


Wrangled data that includes total sales, city,state and order date :
```{r}
glimpse(bike_orderlines_wrangled_tbl)
```

## Analysis of the data
Libraries needed for this section are loaded :
```{r}
library(lubridate)
```
### Visualization of the total sale vs. state
```{r}
  # Manipulate data
  sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Grouping by state and summarizing sales
  group_by(state) %>% 
  summarize(sales = sum(total.price)) %>%
  
  # Currency is adjusted to be euros
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```
                                     
Manipulated data :
```{r}
glimpse(sales_by_state_tbl)
```

Create a plot :
```{r}
sales_by_state_tbl %>%
  
  # Setup canvas with the columns states (x-axis) and sales (y-axis)
  ggplot(aes(y = sales,x = state)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Total sale per state",
    subtitle = "Upward Trend",
    x = "States", # Override defaults for x and y
    y = "Revenue"
  )
```

### Visualization of the total sale per state vs. years
```{r}
# Manipulate data
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
    
    # Select data of interest
    select(order.date, total.price, state) %>%
    mutate(year = year(order.date)) %>%
    
    # Group selected data and summarize year and main catgegory
    group_by(year, state) %>%
    summarise(sales = sum(total.price)) %>%
    ungroup() %>%
    # Formatting
    mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
```

Creation of plots :
```{r plot, fig.width=10, fig.height=7}
sales_by_year_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €"))+
  
  labs(
    title = "Revenue by year and main category",
    subtitle = "Each product category has an upward trend",
    fill = "Main category" # Changes the legend name
  )
```

# Data Acquisition

# Data Wrangling

# Data Visualization

